---
title: "Analysing FIFA Data with the Bayesian LASSO"
subtitle: ""
author: "Jens Klenke"
date: " March 3rd 2020"
output:
  xaringan::moon_reader:
    css: ["default", "assets/sydney-fonts.css", "assets/sydney.css"]
    self_contained: true # if true, fonts will be stored locally
    seal: true # show a title slide with YAML information
    includes:
      in_header: "assets/mathjax-equation-numbers.html"
    nature:
      beforeInit: ["assets/remark-zoom.js", "https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9' #alternatives '16:9' or '4:3' or others e.g. 13:9
      navigation:
        scroll: false #disable slide transitions by scrolling
---
class: inverse

```{r, load_refs, echo=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear", 
           cite.style = 'authoryear', 
           style = "markdown",
           hyperlink = FALSE, 
           dashed = FALSE)
myBib <- ReadBib("assets/example.bib", check = FALSE)


```

# Structure
 

1. Overview of the Data
2. Used Models
3. Estimation
4. Resutls of the Models 
5. Residuals Analysis
6. Conclusion

---
# Original Dataset

* Data from 2015 till 2020 (6 Years)
  + 2019 used for the estimation
  + 2020 to compare the models
* Data for over 15 000 players per year
* 104 variables in the datasets 
  + 12 variables included for the estimation
* Different grading pattern for Goalkeepers

---
# Overview of some important Variables 

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
options(servr.daemon = TRUE)
options(servr.interval = 0.5)

#xaringan::inf_mr()

#### required packages ####
source(here::here("01_code/packages/packages.R"))


```

