---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pvurt

<!-- badges: start -->
<!-- badges: end -->

This package has been created as part of my master thesis. The package has only one user facing function: <tt>computePVale()</tt>, which approximates p-value (cumulative probability) for augmented Dickey-Fuller unit root test based on the distribution of the test statistics. The approximation is based on pre-trained generalized additive logistic model or logistic regression with polynomial terms.

The function can take either a numeric value or the output from the four functions of the following three packages:  <tt>adfTest()</tt> and <tt>unitrootTest()</tt> from <tt>fUnitRoots</tt>, <tt>adf.test()</tt> from <tt>tseries</tt> and, lastly, <tt>ur.df()</tt> from <tt>urca</tt>. If output from any of the function is passed on, <tt>computePVale()</tt> appends its approximation result to the original output. 

## Installation

The package has not been released in [CRAN](https://CRAN.R-project.org). To install use:

``` r
devtools::install_github("mlincon/pvurt")
```
Since the package must be complied, ensure that <tt>Rtools.exe</tt> is installed beforehand.

## Example

```{r example}
library(pvurt)

y <- arima.sim(model = list(order = c(0, 1, 0)), n = 100)

# Test type: with drift and trend
# package: fUnitRoots
library(fUnitRoots)
computePValue(adfTest(y, lags = 3, type = "ct"))

computePValue(unitrootTest(y, lags = 3, type = "ct"))

# package: urca
library(urca)
computePValue(ur.df(y, lags = 3, type = "trend"))
# print summary
summary(computePValue(ur.df(y, lags = 3, type = "trend")))

# package: tseries
library(tseries)
computePValue(adf.test(y, alternative = "stationary", k = 3))

# no packages
tStat <- -2.239
sampleSize <- 100
computePValue(tStat, n = sampleSize, model = "gam", type = "ct")
```
